Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Directionalize paired single-quotes.

\begin{enumerate}
\item The paper describes the Raft RPCs in terms of synchronous stream
    based request/response model where requests and responses are
    automatically correlated together by a lower level of the software
    stack. For example with HTTP 1.0 \cite{http:rfc1945} client
    requests are followed by a server response on any given TCP
    stream. Most remote procedure call mechanims also use
    a synchronous request/response model. %TODO/CITE
    WebRTC DataChannel connections are message based rather than
    request/response stream based. %TODO/CITE
    The original Raft definition of RPC request and response messages
    almost contain enough information to function correctly in an
    environment without builtin request/response correlation such as
    UDP or SCTP when used with reliable transport disabled. %TODO/CITE
    Raft.js includes a small modification to the response RPCs for
    requestVote and appendEntries to add a 'sourceId' field that
    enables the protocol to function with message based transports.
\item The Raft paper is clear that each membership change must be
    delayed until all the previous membership change is committed
    (sequential) \cite[Section~4.1]{raft_thesis:ongaro14}. It is
    implied that the leader node should track all pending membership
    change requests and apply them one at a time.  However, in
    Raft.js, if a client requests a membership change while another
    change request is pending (uncommitted), the leader will reject
    the change request with a status of 'PENDING\_CONFIG\_CHANGE'.
    This keeps the core Raft implementation simpler with the trade-off
    being that the client implementation of membership change requests
    is slightly more complex due to retry logic.
\end{enumerate}

@@

The file `rtc\_server.js` implements the signaling server for the Raft
over WebRTC application. The server extends the PeerJS
`ExpressPeerServer` object in order to provide WebRTC signaling. In
addition to the signaling function, the server also provides the
following service endpoints:

@@

\begin{enumerate}
\item \emph{Term}: the current Raft leadership term.
\item \emph{State}: the current Raft node state (follower, candidate,
    or leader)
\item \emph{Cluster Size}: a count of the current Raft cluster
    membership (number of nodes currently participating in the
    cluster)
\item \emph{Log Length}: number of entries in the transaction log.
\item \emph{Request Votes Sent/Received}: the number of `requestVote`
    RPCs that have been sent from and received by this node.
\item \emph{Append Entries Sent/Received}: the number of
    `appendEntries` RPCs that have been sent from and received by this
    node.
\end{enumerate}

@@

After every change was made to the cluster all the nodes were checked
to ensure that the following steady state properties were observed:
\begin{enumerate}
\item only a single leader
\item all nodes have the same term and transaction log count
\item all non-leader nodes are receiving `appendEntries` RPCs from the leader
\item all nodes have the same cluster membership state
\item the transaction log entries are identical on all nodes
\item the state machine is identical on all nodes
\end{enumerate}

>>>>

\begin{enumerate}
\item The paper describes the Raft RPCs in terms of synchronous stream
    based request/response model where requests and responses are
    automatically correlated together by a lower level of the software
    stack. For example with HTTP 1.0 \cite{http:rfc1945} client
    requests are followed by a server response on any given TCP
    stream. Most remote procedure call mechanims also use
    a synchronous request/response model. %TODO/CITE
    WebRTC DataChannel connections are message based rather than
    request/response stream based. %TODO/CITE
    The original Raft definition of RPC request and response messages
    almost contain enough information to function correctly in an
    environment without builtin request/response correlation such as
    UDP or SCTP when used with reliable transport disabled. %TODO/CITE
    Raft.js includes a small modification to the response RPCs for
    requestVote and appendEntries to add a `sourceId' field that
    enables the protocol to function with message based transports.
\item The Raft paper is clear that each membership change must be
    delayed until all the previous membership change is committed
    (sequential) \cite[Section~4.1]{raft_thesis:ongaro14}. It is
    implied that the leader node should track all pending membership
    change requests and apply them one at a time.  However, in
    Raft.js, if a client requests a membership change while another
    change request is pending (uncommitted), the leader will reject
    the change request with a status of `PENDING\_CONFIG\_CHANGE'.
    This keeps the core Raft implementation simpler with the trade-off
    being that the client implementation of membership change requests
    is slightly more complex due to retry logic.
\end{enumerate}

@@

The file `rtc\_server.js' implements the signaling server for the Raft
over WebRTC application. The server extends the PeerJS
`ExpressPeerServer' object in order to provide WebRTC signaling. In
addition to the signaling function, the server also provides the
following service endpoints:

@@

\begin{enumerate}
\item \emph{Term}: the current Raft leadership term.
\item \emph{State}: the current Raft node state (follower, candidate,
    or leader)
\item \emph{Cluster Size}: a count of the current Raft cluster
    membership (number of nodes currently participating in the
    cluster)
\item \emph{Log Length}: number of entries in the transaction log.
\item \emph{Request Votes Sent/Received}: the number of `requestVote`
    RPCs that have been sent from and received by this node.
\item \emph{Append Entries Sent/Received}: the number of
    `appendEntries' RPCs that have been sent from and received by this
    node.
\end{enumerate}

@@

After every change was made to the cluster all the nodes were checked
to ensure that the following steady state properties were observed:
\begin{enumerate}
\item only a single leader
\item all nodes have the same term and transaction log count
\item all non-leader nodes are receiving `appendEntries' RPCs from the leader
\item all nodes have the same cluster membership state
\item the transaction log entries are identical on all nodes
\item the state machine is identical on all nodes
\end{enumerate}
